---
title: "exploring"
author: "Connor McManus"
date: "DATE"
output: github_document
---

##Part 1

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load the necessary libraries
```{r}
library(tidyverse)
```

Take a look inside your dataset
```{r}
listings
```

### Variation

Perform an analysis of the variation in the "neighbourhood" column. 

```{r}
listings %>%
  count(neighbourhood) %>%
  arrange(desc(n))
ggplot(data = listings) +
  geom_bar(mapping = aes(x = neighbourhood )) 
  
```

* Which values are the most common? Why?
Yau Tsim Mong and Wan Chai because these are centrally-located residential/business areas in Hong Kong.

* Which values are rare? Why? Does that match your expectations?
No values are rare.

* Can you see any unusual patterns? What might explain them?
N/A


Perform an analysis of the variation in the "room_type" column. 

```{r}
listings %>%
  count(room_type) %>%
  arrange(desc(n))
ggplot(data = listings) +
  geom_bar(mapping = aes(x = room_type )) 
```

* Which values are the most common? Why?
Private Room/Entire home/apt because that is what the majority of people offer on AirBnb.

* Which values are rare? Why? Does that match your expectations?
I would expect the probability of an Entire home/apartment to be higher, but due to high real estates in Hong Kong, the high amount of private rooms make sense.

* Can you see any unusual patterns? What might explain them?
No, this seems accurate. 


Perform an analysis of the variation in the "price" column. Make sure to explore different "binwidth" values in your analysis.

```{r}
listings %>%
  count(price) %>%
  arrange(desc(n))
ggplot(data = listings) +
  geom_bar(mapping = aes(x = price ), binwidth = 5) +
  coord_cartesian(xlim = c(0, 3000))
```

* Which values are the most common? Why?
Prices between 25-500 dollars becuase they are the most reasonably priced.

* Which values are rare? Why? Does that match your expectations?
Prices above 500 dollars, which makes sense because these are expensive.

* Can you see any unusual patterns? What might explain them?
No, the patterns seem usual.


Perform an analysis of the variation in the "minimum_nights" column. Make sure to explore different "binwidth" values in your analysis.

```{r}
listings %>%
  count(minimum_nights) %>%
  arrange(desc(n))
ggplot(data = listings) +
  geom_bar(mapping = aes(x = minimum_nights ), binwidth = 5) +
   coord_cartesian(xlim = c(0, 50))
```

* Which values are the most common? Why?
Low values and values at around a month are the most common because a few days or by a monthly basis are what most people use AirBnb for.

* Which values are rare? Why? Does that match your expectations?
Middle values and values after 1 month (30 days) are rare because they are not common amounts of time a person would stay somewhere.

* Can you see any unusual patterns? What might explain them?
No, these patterns seem usual


Perform an analysis of the variation in the "number_of_reviews" column. Make sure to explore different "binwidth" values in your analysis.

```{r}
listings %>%
  count(number_of_reviews) %>%
  arrange(desc(n))
ggplot(data = listings) +
  geom_bar(mapping = aes(x = number_of_reviews), binwidth = 5) +
   coord_cartesian(xlim = c(0, 50))
```

* Which values are the most common? Why?
Lower number of reviews are more common because there is a broad variety of places to stay.

* Which values are rare? Why? Does that match your expectations?
No

* Can you see any unusual patterns? What might explain them?
No, this seems like a usual pattern


Perform an analysis of the variation in the "availability_365" column. Make sure to explore different "binwidth" values in your analysis.

```{r}
listings %>%
  count(availability_365) %>%
  arrange(desc(n))
ggplot(data = listings) +
  geom_bar(mapping = aes(x = availability_365), binwidth = 5) 
   
```

* Which values are the most common? Why?
Ones close to 365 days are most common, this makes sense because as there are a variety of options available, the accommodations are not always used.

* Which values are rare? Why? Does that match your expectations?
Except for a few, no values are overly common which makes sense because all of the accommodations are managed differently.

* Can you see any unusual patterns? What might explain them?
It is a little scattered, which makes sense because people or companies choose to rent out their accommodations for different lengths of time.

##Part 2

What seems to be the most common name (of a person) in the city you selected?
```{r}
listings %>%
  count(host_name) %>%
  arrange(desc(n))
ggplot(data = listings) +
  geom_bar(mapping = aes(x = host_name), binwidth = 5) +
   coord_cartesian(xlim = c(0, 50))
```
Jovee is the most common name.

Do the number of reviews affect the price of the Airbnb? How? Why do you think this happens?
Number of reviews affect the price of an Airbnb because the higher number of reviews (especially good) means there is more feedback and more people will want to stay there, making the price higher.

What type of room tends to have the highest Airbnb price?
```{r}
listings %>%
  count(room_type) %>%
  arrange(desc(n))
ggplot(data = listings) +
  geom_boxplot(mapping = aes(x = reorder(room_type, price, FUN = median), y = price)) + coord_flip()
```

Entire home/apt is the most expensive.

What neighborhood(s) tend to have the highest Airbnb price?
```{r}

ggplot(data = listings) +
   geom_boxplot(mapping = aes(x = reorder(neighbourhood, price, FUN = median), y = price)) + coord_flip()
```
The ares in the Southern part of the city tend to be the most expensive.

Suppose you could purchase a property in the city you selected, and that you could rent it to others as an Airbnb. In what neighborhood would you want to purchase your property? Why? 
I would purchase a property in the Southern area becuase there aren't a lot of properties on Airbnb there, but they have the highest prices.

##Part 3
Parc Inverness, 38 Inverness Road, Kowloon Tong, Kowloon - $16,250,202.00

Visit a real estate website (such as realtor.com) and find a property that is for sale in the neighborhood you selected. Take note of the price and address of the property. 

* Use your dataset to find what the average Airbnb price/night is in the neighborhood you selected.
```{r}
hongkonglistings <- listings %>%
filter(neighbourhood == "Kowloon City") %>%
summarize(
avg_price = mean(price)
)
hongkonglistings
```
Avg_price = $825.33

Use your dataset to find what the average number of available nights per year is for an Airbnb in the neighborhood you selected.
```{r}
hongkong_nbh_npy <- listings %>%
filter(neighbourhood == "Kowloon City") %>%
summarize(
avg_available_nights = mean(availability_365)
)
hongkong_nbh_npy
```
Avg_available nights = 263

Suppose you bought the property you selected above. If you were to rent it as an Airbnb at the average neighborhood price, for the average number of days, how long will it take you to break even?

$84,183.66 per year

It would take 193.03 years or 50,768 nights.

